Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ in each of the
  four regions studied in AIA 171\AA\ (left column) and AIA
  193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
  Model fit parameter values and their 68\% credible intervals are
  quoted in Table \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

Another possible cause of the excess emission is the appearance of
low-temperature emission lines in the AIA passband.  Such lines are
more likely to be due to processes lower down in the solar atmosphere
where the amplitude of three and five minute oscillations is larger.
This is supported by three dimensional magnetohydrodynamic models of
the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
lower temperature lines can be formed in quiet Sun areas that appear
in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
find that the AIA 193\AA\ has more significant contributions from
non-dominant lines when compared to AIA 171\AA.  If this were the
case, then one would expect that the maximum of the ratio between
$G(\nu)/P_{1}(\nu)$ would be higher for the AIA 193\AA\ \PS\ than for
the AIA 171AA\ \PS, which is not obeserved.  However,
\cite{2011ApJ...743...23M} also note that their results are also quite
sensitive to the abundances used in their simulations, which may
explain the differences between their simulations and the observations
presented here.

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}

The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

>>>>

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (blue and red
  lines respectively; see Section \ref{sec:anal} and Appendix
  \ref{sec:app:ind} for more detail).  The AIC and BIC describing the
  preference for model over the other is also indicated in each plot.
  The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
  shown in green; the location of the maximum of their ratio is
  indicated by the green dotted line.  Model fit parameter values and
  their 68\% credible intervals are quoted in Table
  \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

Another possible cause of the excess emission is the appearance of
low-temperature emission lines in the AIA passband.  Such lines are
more likely to be due to processes lower down in the solar atmosphere
where the amplitude of three and five minute oscillations is larger.
This is supported by three dimensional magnetohydrodynamic models of
the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
lower temperature lines can be formed in quiet Sun areas that appear
in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
find that the AIA 193\AA\ has more significant contributions from
non-dominant lines when compared to AIA 171\AA.  If this were the
case, then one would expect that the maximum of the ratio between
$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193}) would be higher
for the AIA 193\AA\ \PS\ than for the AIA 171\AA \PS, which is not
observed.  However, \cite{2011ApJ...743...23M} also note that their
results are also quite sensitive to the abundances used in their
simulations, which may explain the differences between their
simulations and the observations presented here.

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.
